Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-13 paper/paper.Rmd
add group-level CV to table

\begin{table}[h]
  \centering
  \footnotesize
  \caption[t]{Spatiotemporal resampling methods, ordered alphabetically by class name (Notation column). Column count refers to the number of studies which were found to have used this resampling technique until 2021-05.}
  \begingroup
    \begin{tabular}{lllll}
      \\
      Type                            & Name                        & R Package(s)     & mlr3 Notation  & Count\\
      \toprule
      \multirow{6}{*}{Spatial}        & Spatial Buffering           & \specialcell{\pkg{blockCV} \\ \pkg{sperrorest}}    & \specialcell{ \texttt{"spcv\_buffer"} \tablefootnote{\label{ploton2020}\cite{ploton2020}}  \tablefootnote{\label{diesing2020}\cite{diesing2020}} \\  \texttt{"spcv\_disc"} \tablefootnote{\label{endicott2017}\cite{endicott2017}} \tablefootnote{\label{karasiak2021}\cite{karasiak2021}} \tablefootnote{\label{moller2021}\cite{moller2021}}}  & \specialcell{2 \\ 3}   \\
      \cmidrule{2-5}
                                      & Spatial Blocking            & \specialcell{\pkg{blockCV}  \\ \pkg{sperrorest}}  & \specialcell{  \texttt{"spcv\_block"} \tablefootnote{\label{jensen2021}\cite{jensen2021}} \tablefootnote{\label{escobar2021}\cite{escobar2021}} \tablefootnote{\label{stewart2021}\cite{stewart2021}} \\  \texttt{"spcv\_tiles"} \tablefootnote{\label{bebber2017}\cite{bebber2017}} \tablefootnote{\label{brenning2015}\cite{brenning2015}} \tablefootnote{\label{zurell2020}\cite{zurell2020}} }
                                        & \specialcell{28 \\ 4} \\
  \cmidrule{2-5}
                                      & Spatial Clustering          & \pkg{sperrorest} & \texttt{"spcv\_coords"} \tablefootnote{\label{morera2021}\cite{morera2021}} \tablefootnote{\label{geiss2017}\cite{geiss2017}} \tablefootnote{\label{wu2020}\cite{wu2020}} &  21 \\
                                      \cmidrule{2-5}
       & Predefined grouping & \specialcell{\pkg{CAST} \\ \pkg{mlr3}}       & \specialcell{ \texttt{"sptcv\_cstf"} (LLO) \tablefootnote{\label{blothe2021}\cite{blothe2021}} \tablefootnote{\label{dolan2021}\cite{dolan2021}} \tablefootnote{\label{dumke2019}\cite{dumke2019}}  \\ \texttt{"FIXME"}}  & \specialcell{12 \\ -}       \\
      \midrule
      \multirow{2}{*}{Spatiotemporal} & Leave-Location-and-Time-Out & \pkg{CAST}       &  \texttt{"sptcv\_cstf"} \tablefootnote{\label{egli2020}\cite{egli2020}} \tablefootnote{\label{gao2019}\cite{gao2019}} \tablefootnote{\label{reitz2021}\cite{reitz2021}} & 6 \\
                                      & Spatiotemporal Clustering   & \pkg{skmeans}    &  \texttt{"sptcv\_cluto"} &  -  \\
      \midrule
      Feature space                   & Environmental Blocking      & \pkg{blockCV}    &  \texttt{"spcv\_env"} \footref{morera2021}   & 1    \\

@@

### Custom (fixed) Resampling --- mlr3

>>>>

\begin{table}[h]
  \centering
  \footnotesize
  \caption[t]{Spatiotemporal resampling methods, ordered alphabetically by class name (Notation column). Column count refers to the number of studies which were found to have used this resampling technique until 2021-05.}
  \begingroup
    \begin{tabular}{lllll}
      \\
      Type                            & Name                        & R Package(s)     & mlr3 Notation  & Count\\
      \toprule
      \multirow{6}{*}{Spatial}        & Spatial Buffering           & \specialcell{\pkg{blockCV} \\ \pkg{sperrorest}}    & \specialcell{ \texttt{"spcv\_buffer"} \tablefootnote{\label{ploton2020}\cite{ploton2020}}  \tablefootnote{\label{diesing2020}\cite{diesing2020}} \\  \texttt{"spcv\_disc"} \tablefootnote{\label{endicott2017}\cite{endicott2017}} \tablefootnote{\label{karasiak2021}\cite{karasiak2021}} \tablefootnote{\label{moller2021}\cite{moller2021}}}  & \specialcell{2 \\ 3}   \\
      \cmidrule{2-5}
                                      & Spatial Blocking            & \specialcell{\pkg{blockCV}  \\ \pkg{sperrorest}}  & \specialcell{  \texttt{"spcv\_block"} \tablefootnote{\label{jensen2021}\cite{jensen2021}} \tablefootnote{\label{escobar2021}\cite{escobar2021}} \tablefootnote{\label{stewart2021}\cite{stewart2021}} \\  \texttt{"spcv\_tiles"} \tablefootnote{\label{bebber2017}\cite{bebber2017}} \tablefootnote{\label{brenning2015}\cite{brenning2015}} \tablefootnote{\label{zurell2020}\cite{zurell2020}} }
                                        & \specialcell{28 \\ 4} \\
  \cmidrule{2-5}
                                      & Spatial Clustering          & \pkg{sperrorest} & \texttt{"spcv\_coords"} \tablefootnote{\label{morera2021}\cite{morera2021}} \tablefootnote{\label{geiss2017}\cite{geiss2017}} \tablefootnote{\label{wu2020}\cite{wu2020}} &  21 \\
                                      \cmidrule{2-5}
       & Group-Level CV & \specialcell{\pkg{CAST} \\ \pkg{mlr3}}       & \specialcell{ \texttt{"sptcv\_cstf"} (LLO) \tablefootnote{\label{blothe2021}\cite{blothe2021}} \tablefootnote{\label{dolan2021}\cite{dolan2021}} \tablefootnote{\label{dumke2019}\cite{dumke2019}}  \\ \texttt{"custom\_cv"} \tablefootnote{\label{brenning2006}\cite{brenning2006}} \tablefootnote{\label{pena2015}\cite{pena2015}}} & \specialcell{12 \\ 2}       \\
      \midrule
      \multirow{2}{*}{Spatiotemporal} & Leave-Location-and-Time-Out & \pkg{CAST}       &  \texttt{"sptcv\_cstf"} \tablefootnote{\label{egli2020}\cite{egli2020}} \tablefootnote{\label{gao2019}\cite{gao2019}} \tablefootnote{\label{reitz2021}\cite{reitz2021}} & 6 \\
                                      & Spatiotemporal Clustering   & \pkg{skmeans}    &  \texttt{"sptcv\_cluto"} &  -  \\
      \midrule
      Feature space                   & Environmental Blocking      & \pkg{blockCV}    &  \texttt{"spcv\_env"} \footref{morera2021}   & 1    \\

@@

#### Custom (fixed) Resampling --- mlr3
